Resonant Scattering in a Uniform Sphere with Large Optical Depth

### 2021-10-06 ms.tex
Adding L luminosity parameter description after Eq. 2, adding definition of x (spatial variable)

Starting with the full transfer equation, Eq. \ref{eq:finaleqn}, with no photon destruction and a photon emission term given by Eq. \ref{eq:jem}, the steady-state transfer equation is
\be
\nabla^2 J + \left( \frac{k}{\Delta} \right)^2 \frac{\partial^2 J}{\partial \sigma^2} & = & 
- \frac{ \sqrt{6} kL}{4\pi \Delta^2} \delta^3(\vec{x} - \vec{x}_s) \delta (\sigma - \sigma_{\rm s}).
\label{eq:rt_no_destr}
\ee
where $J$ is the mean intensity, $\sigma$ represents a change of variables in photon frequency (Eq. \ref{eq:change_of_variables}) and $\sigma_s$ is is the photon frequency of the source. $\sigma_s$ is interchangeable with $x_s$ and $\nu_s$ in Doppler units or Hz, respectively. The boundary condition that there is no incoming intensity at the surface \citep{1986rpa..book.....R} can be written as
\be
J & = & \sqrt{3} H
\label{eq:bc}
\ee
at $r=R$.

>>>>

Starting with the full transfer equation, Eq. \ref{eq:finaleqn}, with no photon destruction and a photon emission term given by Eq. \ref{eq:jem}, the steady-state transfer equation is
\be
\nabla^2 J + \left( \frac{k}{\Delta} \right)^2 \frac{\partial^2 J}{\partial \sigma^2} & = & 
- \frac{ \sqrt{6} kL}{4\pi \Delta^2} \delta^3(\vec{x} - \vec{x}_s) \delta (\sigma - \sigma_{\rm s}).
\label{eq:rt_no_destr}
\ee
where $J$ is the mean intensity, $L$ is a luminosity input, $\sigma$ represents a change of variables in photon frequency (Eq. \ref{eq:change_of_variables}), and $\sigma_s$ is is the photon frequency of the source. $\sigma_s$ is interchangeable with $x_s$ and $\nu_s$ in Doppler units or Hz, respectively. The spatial variable is $\vec{x}$ and $\vec{x}_s$ is the position of the source. The boundary condition that there is no incoming intensity at the surface \citep{1986rpa..book.....R} can be written as
\be
J & = & \sqrt{3} H
\label{eq:bc}
\ee
at $r=R$.
